Holomorphic field theories and higher algebra

### 2022-09-30 draft.tex
edits to seiberg

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
%We will denote this theory by $\cT(N,F)$.
\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}
%, denoted $\cT(N,F, V_M, W)$, 
is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
\mu \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad \nu \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, \Tilde{Q}, \mu) .
\] 
Notice that to write down the superpotential term we are utilizing the holomorphic volume form $\Omega_X = \d^2 z$. 
\end{dfn}

@@

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
\brian{I don't like this notation, its confusing since it looks like symplectic reduction which has already appeared. 
What about $[V/G]$?} \owen{I'm happy to do that, but symplectic reduction is the GIT quotient.}
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
(Note that the font of M changes between stack and space.)

@@

\begin{rmk}
In the physics literature this isomorphism is given by explicitly matching gauge-invariant functions, 
which are often called mesons or baryons, 
as they can be identified with the data that identifies such particles.
These meson and baryons are precisely the usual generators of the ring of invariant functions, 
so an isomorphism of generators determines the desired isomorphism of rings. 
One must check that the relations are satisfied;
this requirement explains the superpotential on the magnetic side.
\end{rmk}

@@

The quarks of the electric theory take values in $\Hom(\CC^F, \CC^N)$ and hence have a canonical action of $SL(F)$ by precomposition.
We view each factor $\CC$ inside $\CC^F$ as a different ``flavor'' of quark, so this action mixes flavors.
The antiquarks take values in $\Hom(\CC^N, \CC^F)$ and so have a canonical action of $SL(F)$ by postcomposition.
The action functional is invariant for this action, and thus $SL(F)$ acts naturally on the space of solutions to the equations of motion.
This symmetry is known as {\em flavor} symmetry.
The magnetic theory has an analogous flavor symmetry, where $SL(F)$ acts on the mesons by conjugation.
\owen{Right?}

@@

For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,*}(\CC^2, \sl(F))$, 
which we call a $2$-dimensional holomorphic current algebra.
It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.

%The holomorphic background field $\fa = (\fa_i^j) \in \Omega^{0,\bu}(\CC^2 , \sl(N_f))$ naturally couples to both the electric and magnetic theory in the following ways:
%\[
%I^F_\sfE = \int P_j \fa_i^j Q^i , \qquad I^F_\sfM = \int \Tilde{p}_j \sfa_j^i \Tilde{q}^j + \int L^k_j \sfa_i^j M^i_k . 
%\]
%
%This determines a classical symmetry of both sides of the duality by the local Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(N_f))$. 
%In particular, the two state spaces form a module for the $S^3$-current algebra $\sfA_2 \otimes \sl(N_f)$ at the classical level.

A natural question is whether this symmetry persists at the quantum level. 
The answer is {\em yes}, but on both sides of the duality one must use a central extension of the current algebra as an $L_\infty$ algebra.
The extension arises because the symmetry has an anomaly under quantization (on either side of the duality),
and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - \{0\}$.)

\begin{prop}
There is an anomaly at the quantum level for the holomorphic flavor symmetry action for both the electric and magnetic theories,
and they agree: they are labeled by the same cocycle 
\[
\theta_\sfE = \theta_\sfM.
\] 
In particular, the state spaces $\sfV_\sfE, \sfV_\sfM$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(N_f)}_{2,\theta}$.
\end{prop}

@@

\begin{proof}[Sketch of proof]
The argument boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,*}(\CC^2, \sl(F))$, which we treat as a background gauge field.
In formulas, we couple the current algebra to both the electric and magnetic theory via interactions
\[
I^F_\sfE = \int (R, \sfa Q)  \qquad\text{and}\qquad I^F_\sfM = \int (\check{R}, \sfa \check{Q}) + \int (\check{\nu}, \sfa \check{\mu}),
\]
where we use parentheses $(-,-)$ to denote the pairings in BF and $\beta\gamma$ theories.

@@

\begin{thm}[\cite{SWsuco}] 
\label{thm:swsuco}
Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
This local Lie algebra is a classical symmetry of any holomorphic QCD theory. 
\end{thm}

@@

On the gauge fields, this naive action is consistent with the one present in the untwisted theory. 
For the matter fields, however, the action at the untwisted level is {\em not} compatible with this naive one. 
The issue can be seen already just for the holomorphic Euler vector field.
Naively, the field $Q = z_1^n z_2^m \otimes v \in \Omega^0 (\CC^2$ transforms like $\Delta^{hol}(Q) = (n+m) Q$;
but to be compatible with dimension scaling in the untwisted theory, one needs
\[
\Delta^{hol}(Q) = \left(n + m + \frac23\right) Q .
\]
What this constraint means is that, as a representation for holomorphic vector fields, the quark fields $Q$, $R$ take values in some interesting line bundle and not in the trivial vector bundle.  
In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of \cite{WittenTwist}, 
one finds that the quark fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes V_Q 
\] 
and
\[ P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes V_Q^*,
\]
and similarly for the antiquark ${Q}^\dag$ and~${P}^\dag$.

\begin{prop}
For either an electric theory $\cT_{\sfE}(F,N)$ or magnetic theory $\cT_{\sfM}(F,N)$,
the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
has an anomaly to exist at the quantum level. 
It is proportional to the local functional
\[
\left(F - 3N\right) \frac12 \int \partial_{z_i} X_i \op{Tr} (\partial A \, \partial A)  .
\]
where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.

@@

\owen{I'm not clear how this intertwines with duality. It looks like the anomalies don't match?}

>>>>

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
\brian{BTW, I think you've now switched from lower case $r,q$ for antiquarks to $R^\dag, Q^\dag$, is that right?
}
%We will denote this theory by $\cT(N,F)$.
\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}
%, denoted $\cT(N,F, V_M, W)$, 
is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
\mu \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad \nu \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, Q^\dag, \mu) .
\] 
Notice that to write down the superpotential term we are utilizing the holomorphic volume form $\Omega_X = \d^2 z$. 
\end{dfn}

@@

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
(Note that the font of M changes between stack and space.)

@@

\begin{rmk}
In the literature this isomorphism is given by explicitly matching gauge-invariant functions, 
which are often called mesons or baryons, 
as they can be identified with the data that identifies such particles.
These meson and baryons are precisely the usual generators of the ring of invariant functions, 
so an isomorphism of generators determines the desired isomorphism of rings. 
One must check that the relations are satisfied;
this requirement explains the superpotential on the magnetic side.
\end{rmk}

@@

The quarks of the electric theory take values in $\Hom(\CC^F, \CC^N)$ and hence have a canonical action of $SL(F)$ by precomposition.
We view each factor $\CC$ inside $\CC^F$ as a different ``flavor'' of quark, so this action mixes flavors.
The antiquarks take values in $\Hom(\CC^N, \CC^F)$ and so have a canonical action of $SL(F)$ by postcomposition.
The action functional is invariant for this action, and thus $SL(F)$ acts naturally on the space of solutions to the equations of motion.
This symmetry is known as {\em flavor} symmetry.
The magnetic theory has an analogous flavor symmetry, where $SL(F)$ acts on the mesons by conjugation.

@@

For holomorphic QCD theories, the infinitesimal flavor symmetry by the Lie algebra $\sl(F)$ enhances to a symmetry for the infinite-dimensional dg Lie algebra $\Omega^{0,\bu}(\CC^2, \sl(F))$, 
which we call a $2$-dimensional holomorphic current algebra.
It acts by wedging the forms and applying $\sl(F)$ to the relevant vector space, such as~$\Hom(\CC^F,\CC^N)$.
On local observables, the $S^3$-mode algebra $\lie{sl}(F) \otimes \sfA_2$ (which is the algebraic version of $\sl(F) \otimes \Omega^{0,\bu}(\CC^2 - 0)$) acts at the classical level.

A natural question is whether this symmetry persists at the quantum level. 
The answer is {\em yes}, but on both sides of the duality one must use a central extension of the current algebra as an $L_\infty$ algebra.
The extension arises because the symmetry has an anomaly under quantization (on either side of the duality),
and this anomaly is determined by an  invariant cubic polynomial $\theta_\sfE$, $\theta_\sfM$, respectively, on the Lie algebra~$\sl(F)$. 
(In terms of Section \owen{cross ref}, these determine higher Kac--Moody algebras $\Hat{\sl(N_f)}_{2,\theta_{\sfE}}, \Hat{\sl(N_f)}_{2,\theta_{\sfM}}$ when studying the theories on the punctured space~$\CC^2 - 0$.)

\begin{prop}
There is an anomaly at the quantum level for the holomorphic flavor symmetry action for both the electric and magnetic theories,
and they agree: they are labeled by the same cocycle 
\[
\theta_\sfE = \theta_\sfM.
\] 
In particular, the local observables $\Obs_{\sfE} (0), \Obs_{\sfM} (0)$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(F)}_{2,\theta}$ which is a central extension of the $S^3$-mode algebra $\sl(F) \otimes \sfA_2$.
\end{prop}

@@

\begin{proof}[Sketch of proof]
The argument boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,\bu}(\CC^2, \sl(F))$, which we treat as a background gauge field.
In formulas, we couple the current algebra to both the electric and magnetic theory via interactions
\[
I^F_\sfE = \int (R, \sfa Q)  \qquad\text{and}\qquad I^F_\sfM = \int (\check{R}, \sfa \check{Q}) + \int (\check{\nu}, \sfa \check{\mu}),
\]
where we use parentheses $(-,-)$ to denote the pairings in BF and $\beta\gamma$ theories.

@@

\begin{thm}[\cite{SWsuco}] 
\label{thm:swsuco}
Consider the local Lie algebra $\Omega^{0,\bu}(\CC^2, \T^{1,0})$ that resolves the Lie algebra of {\em all} holomorphic vector fields on $\CC^2$. 
This local Lie algebra is a classical symmetry of the holomorphic QCD theory (in particular, the holomorphic twist of any four-dimensional supersymmetric QCD). 
\end{thm}

@@

On the gauge fields, this naive action is consistent with the one present in the untwisted theory. 
For the matter fields, however, the action at the untwisted level is {\em not} compatible with this naive one. 
The issue can be seen already just for the holomorphic Euler vector field.
Naively, the field $Q = z_1^n z_2^m \otimes v$ transforms like $\Delta^{hol}(Q) = (n+m) Q$;
but to be compatible with dimension scaling in the untwisted theory, one needs
\[
\Delta^{hol}(Q) = \left(n + m + \frac23\right) Q .
\]
What this constraint means is that, as a representation for holomorphic vector fields, the quark fields $Q$, $R$ take values in some interesting line bundle and not in the trivial vector bundle.  
In fact, if one keeps track of the appropriate {\em twisting homomorphism} in the style of \cite{WittenTwist}, 
one finds that the quark fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{1/3}) \otimes V_Q 
\] 
and
\[ P \in \Omega^{0,\bu}(\CC^2 , K_{\CC^2}^{2/3}) \otimes V_Q^*,
\]
and similarly for the antiquarks ${Q}^\dag$ and~${P}^\dag$.

\begin{prop}
For either an electric theory $\cT_{\sfE}(F,N)$ or magnetic theory $\cT_{\sfM}(F,N)$,
the symmetry by the local Lie algebra of holomorphic vector fields, described by Theorem~\ref{thm:swsuco}
has an anomaly to exist at the quantum level. 
It is proportional to the local functional
\[
 \frac{F - 3N}{2} \int \partial_{z_i} X_i \op{Tr} (\partial A \, \partial A)  .
\]
where $X = X_i \partial_{z_i} \in \Omega^{0,\bu}(\CC^2, \T_{\CC^2}^{1,0})$ denotes a Dolbeault form-valued vector field and $A$ is a gauge field.

@@

\owen{I'm not clear how this intertwines with duality. It looks like the anomalies don't match?}
\brian{
I'm not sure how to interpret this, so we may want to leave it out. 
The thing I don't understand is what we can glean about `scale' at the level of the holomorphic twist. 
I was hopeful about this computation since it's curious that this anomaly vanishes precisely at the upper bound of the `conformal window', but I'm not sure how to see the full window at the level of the twist. 
Any thoughts?
}
